Malacology: A Programmable Storage System Built on Ceph

### 2016-05-09 paper/paper.tex
zlog notes
Signed-off-by: Noah Watkins <noahwatkins@gmail.com>

\subsection{ZLog: A Distributed Shared-Log}

@@

@@

\subsubsection{Sequencer recovery with
MDS}\label{sequencer-recovery-with-mds}

\subsubsection{MDS Policy for Revoking
Capability}\label{mds-policy-for-revoking-capability}

@@

\subsubsection{Mantle Balancing Policies to Migrate
Sequencers}\label{mantle-balancing-policies-to-migrate-sequencers}

>>>>

\subsection{ZLog: A Fast Distributed Shared-Log}

@@

\subsubsection{Sequencer}

@@

@@

Mantle is used to implement a zlog file type specific policy for maximizing
throughput to the sequencer by migration the resource between metadata servers.

Sequencer recovery is handled by tapping into existing recovery mechanisms
that recover inode state. file type specific recovery augments the existing
recovery procedure.
